---
title: "General Social Survey (Part 1)"
author: "David Jackson"
date: "2/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DBI)
library(odbc)
library(tidyverse)
library(stringr)
library(gssr)
library(janitor)
library(lubridate)
library(tidytext)
library(wordcloud)
```

## General Social Survey (1972 - 2021)

"Since 1972, the General Social Survey (GSS) has provided politicians, policymakers, and scholars with a clear and unbiased perspective on what Americans think and feel about such issues as national spending priorities, crime and punishment, intergroup relations, and confidence in institutions." (https://gss.norc.org/)

## Import Data and Codebook

```{r }
rm(list = ls())
data(gss_all) # Grab data
data(gss_doc) # Grab code book
data(stop_words)
gss_all <- gss_all %>% janitor::clean_names()

```

## Begin Text Mining and Sentiment Analysis

```{r}

gss_tokens <- gss_doc %>% tidytext:: unnest_tokens(description,text,to_lower = TRUE)
```
```{r}

stop_words <- stop_words %>% rename(description = word)
```
```{r}
gss_tokens_clean <-  gss_tokens %>% anti_join(stop_words)
```

### Tokens with stop words

```{r}
gss_tokens %>% count(description,sort =T)
```

### Tokens without stop words

```{r}
gss_tokens_clean <-  gss_tokens %>% anti_join(stop_words)
```

```{r}
gss_tokens_clean %>% count(description,sort =T) %>% top_n(25) %>%
  ggplot() + geom_col(aes(x=reorder(description,n),y=n)) +
  coord_flip() + labs(title ="Top 25 Token / Words",x="Words / Tokens",
                      y="Word Counts")

```

### Unnest Two Ngrams


```{r}

gss_sentences <- gss_doc %>% 
  tidytext:: unnest_tokens(description,text,to_lower = TRUE,token = "ngrams")
```

```{r}
gss_sentences_clean <-  gss_sentences %>% anti_join(stop_words) %>%
  with(wordcloud(description, n, max.words = 100))
  
```

```{r}
gss_sentences_clean %>%  str_extract(description,"[a-z]+") %>% count(description,sort =T)

```

### Pull Decriptions containing sports, religion, politics

```{r}
con <- DBI::dbConnect(odbc::odbc(), 
                      Driver = "SQL Server", 
                      Server = "localhost\\SQLEXPRESS", 
                      Database = "GSS", 
                      Trusted_Connection = "True")

```


```{r}
gss_test <- gss_doc %>% filter(str_detect(string = description, pattern = c("sport","relig","polit")))
```
```{r}
gss_test <- gss_test %>% select(id,description)
dbWriteTable(con, "gss_test",gss_test ,overwrite=TRUE)
```
```{r}
gss_vars <- gss_get_marginals(varnames =gss_test$id,data = gss_doc,margin = marginals) %>%
  filter(!label %in% c("Total","DK","IAP"))
```

### Uplead data in 1000 column chucks

```{r}
t1 <- gss_all %>% select(1:1000)
dbWriteTable(con, "t1",t1 ,overwrite=TRUE)

## Break down Survey into tabl of 1000 columns (+2)
t2 <- gss_all %>% select(1,2,1001:2000)
dbWriteTable(con, "t2",t2 ,overwrite=TRUE)
##
```
```{r}
t3 <- gss_all %>% select(1,2,2001:3000)
dbWriteTable(con, "t3",t3 ,overwrite=TRUE)
##
t4 <- gss_all %>% select(1,2,3000:3999)
dbWriteTable(con, "t4",t4 ,overwrite=TRUE)
##
```

```{r}
t5 <- gss_all %>% select(1,2,4000:4999)
dbWriteTable(con, "t5",t5 ,overwrite=TRUE)
##
t6 <- gss_all %>% select(1,2,5000:5999)
dbWriteTable(con, "t6",t6 ,overwrite=TRUE)
##
t7 <- gss_all %>% select(1,2,6000:6110)
dbWriteTable(con, "t7",t7 ,overwrite=TRUE)
##

```

