---
title: 'GSS: Part 2'
author: "David Jackson"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(forecast)
library(stringr)
library(gssr)
```

## R Markdown

## Load GSS Data

```{r}
rm(list = ls())
data(gss_all) # survey data
data(gss_doc) # code book
gss_all <- gss_all %>% janitor::clean_names()
region_agewed  <- gss_all %>% select(year,id,race,sex,age,
                                  agewed, region, relig, jew, conpresy)
```
```{r}
write.csv(region_agewed,file="gss_agewed_jew.csv",row.names = F)
gss_agewed_jew <- read_csv("./gss_agewed_jew.csv")
```

## Data Wranging


```{r}
gss_agewed_jew$sex <-recode(gss_agewed_jew$sex,`1` ="Male",`2` = "Female")

gss_agewed_jew$race <- 
recode(gss_agewed_jew$race,`1`="White",`2`="Black",`3` = "Other")
```

```{r}
## Confidence in Press: Not Enough Data
gss_agewed_jew$conpresy <-  recode(gss_agewed_jew$conpresy,`1`="COMPLETE CONFIDENCE",`2` ="COMPLETE CONFIDENCE",`3` = "COMPLETE CONFIDENCE",`4` = "Not Opion",
                                   `5` = "LITTLE CONFIDENCE",
                                    `6` = "NO CONFIDENCE",
                                   `7`="NO CONFIDENCE")
```

```{r}
agewed_lookup$value <- as.numeric(agewed_lookup$value)
gss_region <- agewed_lookup %>% filter(variable =="region") %>%  select(value,label) %>% rename(region = value) %>%
  inner_join(gss_agewed_jew)
```

```{r}
# agewed_lookup$value <- as.numeric(agewed_lookup$value)
gss_religion <- agewed_lookup %>% filter(variable =="jew") %>%  select(value,label) %>% rename(jew = value) %>%
  inner_join(gss_region,by="jew") 
```

```{r}
# agewed_lookup$value <- as.numeric(agewed_lookup$value)
gss_religion <- agewed_lookup %>% filter(variable =="relig") %>%  select(value,label) %>% rename(relig = value) %>%
  inner_join(gss_religion,by="relig") %>% rename(religion = label.x) 
```

## Grab Details about Variable
```
```{r}
agewed_lookup <- gss_get_marginals(varnames = c("agewed","region","relig","jew","conpresy"), data = gss_doc, margin = marginals) %>% select(variable,value,label) %>% 
  filter(label !="Total", label !="DK",label !="IAP") %>% na.omit()
```

## Average Age When Married

```{r}

gss_agewed_jew %>% select(race,year,agewed) %>% na.omit() %>%
group_by(year,sex) %>% summarise(sum_age = mean(agewed)) %>%
  ggplot() + geom_line(aes(x=year,y=sum_age,group = sex,col=factor(sex)),lwd=1) +
  labs(title ="Average Age When  Married",x ="Survey Year"
  ,y="Average Age Wed")
```
```{r}

gss_agewed_jew %>% filter(race !="Other") %>% select(sex,race,year,agewed) %>% na.omit() %>%
group_by(year,sex,race) %>% summarise(sum_age = mean(agewed)) %>%
  ggplot() + geom_point(aes(x=year,y=sum_age,group = race,col=factor(race)),lwd=1) +
  labs(title ="Average Age When  Married By Race and Sex",x ="Survey Year"
  ,y="Average Age Wed") + facet_wrap(~sex) +
  geom_smooth(aes(x=year,y=sum_age))
```

##  CONFIDENCE IN The PRESS

```{r}
gss_agewed_jew %>% count(conpresy,sort =T)
```

